Structured Versus Decorated Cospans

### 2022-04-22 cospans_arxiv_3.tex
third arXiv version = version that will appear in the journal

\documentclass[ a4paper, onecolumn, superscriptaddress,10pt, accepted=2022-03-25, issue=3, volume=4, shorttitle=papers/compositionality-4-3 ]{compositionalityarticle}
\pdfoutput=1

>>>>

\documentclass[ a4paper, onecolumn, superscriptaddress,10pt, accepted=2022-02-14, issue=3, volume=4, shorttitle=papers/compositionality-4-3 ]{compositionalityarticle}
\pdfoutput=1
